---
title             : "Lab 8 Group Git Project"
shorttitle        : "Lab 8"

author: 
  - name          : "Kathryn Denning"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kdenning@uorego.edu"
  - name          : "Tamara Niella"
    affiliation   : "1"
  - name          : "Karlena Ochoa "
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"




abstract: |
  This is where we would write our abstract. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Lab 8, Git"
wordcount         : 

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, echo=FALSE, message=FALSE}
library("papaja")
library(rio)
library(tidyverse)
library(here)
library(magrittr)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(fig.width=6.5, fig.height=8) 

data<- import(here("DATA", "star2.csv"))

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load, include=FALSE }



```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

In @batson1997 we learn that empathy is actually perspective taking (cool!). And in [@epley2004] we learn people are selfish when perspective taking (because they are egocentric!).

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("references.bib")` for all our analyses.


# Results
```{r summary statistics, echo=FALSE}
results <- data %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss), math_sd=sd(tmathss), rdg_mean=mean(treadss), rdg_sd=sd(treadss))

kable(results, "latex", booktabs=TRUE)
```

```{r plot, echo=FALSE}
data$frl <- as.factor(data$frl)
p<- ggplot(data, aes(totexp, tmathss, color=frl))+
  geom_point(color="gray")+
  theme_minimal()+
  geom_smooth(method="lm")+
  labs(title="Relation between teacher experience and math scores", subtitle= "Separate regression lines displaed by free/reduced lunch status", x= "Teacher Experience (years)", y="Total Math Scale Score")+
  scale_color_manual(name="Lunch status", labels=c("Free/Reduced Price Meals", "Paid Meals"), values = c("#F8766D", "#00BFC4"))

p+ theme(legend.position="bottom")


```


# Discussion

As we can see in the plot, there is a positive relation between  Teacher's years of experience and Total Math Scores, Math scores are generally higher when there is Free/reduced price meals than when meals are paid. 

\newpage

# References
```{r create_references, warning=FALSE}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
